---
title: "Final Project"
author: "Grace DesJardins"
format: pdf
editor: visual
---

## Wikipedia Web Scraping

```{r, results='hide'}
library(xml2)
library(rvest)
library(tidyverse)
```

Starting with the following page, Top 25 Report/October 6 to 12, 2024. <https://en.wikipedia.org/wiki/Wikipedia:Top_25_Report/October_6_to_12,_2024>

The ultimate goal is to gather the table and convert it to a `data.frame`.

As a first step, read in the html page as an R object. Extract the tables from this object (using the `rvest` package) and save the result as a new object. Follow the instructions if there is an error. Use `str()` on this new object -- it should be a list. Try to find the position of the table in this list since we need it in the next step.

```{r}
# reading in the html page as an R object
url <- read_html("https://en.wikipedia.org/wiki/Wikipedia:Top_25_Report/October_6_to_12,_2024")
```

```{r}
# extracting the tables from url
tables <- url %>% 
  html_table(fill = TRUE)
```

```{r}
# using str() on tables (a list)
str(tables)
```

Extract the table from the list and save it as another object. You can use subsetting via `[[…]]` to extract pieces from a list. Print the result.

```{r}
# extracting the table and saving it as "top_25"
top_25 <- tables[[1]]
# printing the result
print(top_25)
```

You will see that the table needs some additional formatting. We only want rows and columns with actual values.

```{r}
top_25 <- top_25[, -c(3,5)]
top_25
```
